A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-16 sections/conclusion/main.tex
Change overall structure (#35)
* Change the overall structure

New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

* Minor changes

- Minor changes to sections and subsections
- Move figure from game section to queueing section

* Fix failing proselint task

Clean the text before running proselint on it. Currently just removes
`\centering' command from .tex files

* Modify introduction section

* Restructure game theoretic model

This study explores a generic 3-player game theoretic model between the 
decision makers of two queueing systems and a service that distributes 
individuals to these two systems (section \ref{sec:model_overview}).
It also describes the construction of the underlying queueing theoretic model 
that has a tandem buffer and a single service centre (section 
\ref{sec:queueing_model}).
Furthermore, the formulas for the performance measures of the queueing model 
are also derived (sections \ref{sec:waiting_time}, \ref{sec:blocking_time}, 
\ref{sec:proportion_within_target}). 
This novel queuing model is the first contribution of the paper.
The game theoretic model is then applied to a healthcare scenario by looking at
the interface between the EDs and the EMS.
The inefficiencies that emerge from the perspective of the EMS were explored 
along with ways to apply some incentive mechanisms to improve them.
The key findings from this paper that were observed when playing the game
between two EDs and the EMS are:
\begin{itemize}
    \item Inefficiencies can be learned and emerge naturally
    \item Targeted incentivisation of behaviours can help escape inefficiencies
\end{itemize}
The former relates to the results of asymmetric replicator dynamics that showed 
that inefficient scenarios can arise by playing the game while the latter 
implies that the learned inefficiencies can be escaped by carefully applying 
certain incentives to the players.
This applied game theoretic model is the second main contribution of this paper.

>>>>

This study explores a generic 3-player game theoretic model between the 
decision makers of two queueing systems and a service that distributes 
individuals to these two systems (section \ref{sec:model_overview}).
It also describes the construction of the underlying queueing theoretic model 
that has a tandem buffer and a single service centre (section 
\ref{sec:queueing_model}).
Furthermore, the formulas for the performance measures of the queueing model 
are also derived (sections \ref{sec:waiting_time}, \ref{sec:blocking_time}, 
\ref{sec:proportion_within_target}). 
This novel queuing model is the first contribution of the paper.
The game theoretic model is then applied to a healthcare scenario by looking at
the interface between the EDs and the EMS.
The inefficiencies that emerge from the perspective of the EMS were explored 
along with ways to apply some incentive mechanisms to improve them.
The key findings from this paper that were observed when playing the game
between two EDs and the EMS are:
\begin{itemize}
    \item Inefficiencies can be learned and emerge naturally
    \item Targeted incentivisation of behaviours can help escape inefficiencies
\end{itemize}
% TODO: Make sure this is consistent with `intro' and `lit review' sections
The former relates to the results of asymmetric replicator dynamics that showed 
that inefficient scenarios can arise by playing the game while the latter 
implies that the learned inefficiencies can be escaped by carefully applying 
certain incentives to the players.
This applied game theoretic model is the second main contribution of this paper.

### 2022-03-16 sections/introduction/main.tex
Change overall structure (#35)
* Change the overall structure

New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

* Minor changes

- Minor changes to sections and subsections
- Move figure from game section to queueing section

* Fix failing proselint task

Clean the text before running proselint on it. Currently just removes
`\centering' command from .tex files

* Modify introduction section

* Restructure game theoretic model

There are numerous news articles that focus on the problems that arise when 
ambulances stay blocked outside of the hospital for a long amount of 
time~\cite{dailyrecords, staffordshirelive}.
Some news reports also comment on the long idle time of ambulances when 
they are not in use~\cite{herefordtimes} and there are several reports of 
examples where this became an issue for new patients~\cite{southwalesargus}.
A particular article looked into this problem from the point of view of an 
ambulance paramedic:

@@

% Major contributions
The novelty of our research contribution in this paper is to consider:
\begin{itemize}
    \item A queueing model with 2 consecutive waiting spaces where one would 
    serve as a parking space for the ambulances
    \item Performance measure formulas for the queueing model
    \item A 3-player game theoretic model between the EMS and two EDs
    \item The emergence of gaming behaviour between EDs and the EMS.
\end{itemize}
Specifically, our focus is on the construction of a 3-player game theoretic 
model between two queueing systems and a service that distributes individuals
to them. 
The resultant model is then used to explore the emergent dynamics between 
the three players.
This study explores two new concepts: getting performance measures for a new
queueing theoretic model with a parking space and a service centre and
using a learning algorithm to model the emergence of behaviour.
The developed theoretical model is illustrated through the application to 
a healthcare system of two EDs and the EMS, exploring the inefficiencies that 
emerge and ways to apply some incentive mechanisms to improve them.
The EDs are modelled as two queueing systems each with a tandem buffer and a 
service centre.
The performance measures are then used as the utilities of the game.
The novelty of the queueing model here is a contribution not only the game 
theoretic literature but also to the queueing theoretic literature.
To the authors knowledge, no such model of a tandem queueing model with a pair 
of parameters for the buffer has been considered.
Although our research is motivated by the particular EMS-ED example, our 
developed modelling framework and behavioural insights has application to 
similar systems across a range of sectors and settings.

% Sign posting
This paper consists of two main sections.
The first section presents a novel queueing model for a hospital with two
types of patients and two waiting zones.
A detailed description of how to acquire the performance measure formulas of 
such queueing system is given.
The next section gives an overview of the game theoretic model and several
theoretic results pertaining to the performance measures of this model which 
are used to build the utilities of the game.

>>>>

There are numerous news articles that focus on the complexity that arises when
ambulances stay blocked outside of the hospital for a long amount of 
time~\cite{dailyrecords, staffordshirelive}.
Some news reports comment on the long idle time of ambulances when
they are not in use~\cite{herefordtimes} and there are several reports of 
examples where this became an issue for new patients~\cite{southwalesargus}.
A particular article looked into this problem from the point of view of an 
ambulance paramedic:

@@

% Major contributions
The major contributions of this paper are:
\begin{itemize}
    \item A queueing model with 2 consecutive waiting spaces where one would 
    serve as a parking space for the ambulances
    \item Analytic performance measure formulas for the queueing model
    \item A 3-player game theoretic model between the EMS and two EDs
    \item Numerical experiments showing emergent behaviour of gaming between
    EDs and the EMS.
\end{itemize}
Specifically, our focus is on the construction of a 3-player game theoretic 
model between two queueing systems and a service that distributes individuals
to them. 
The resultant model is then used to explore the emergent dynamics between 
the three players.
This study explores two new concepts: getting performance measures for a new
queueing theoretic model with a parking space and a service centre and
using a learning algorithm to model the emergence of behaviour.
The developed theoretical model is illustrated through the application to 
a healthcare system of two EDs and the EMS, exploring the inefficiencies that 
emerge and ways to apply some incentive mechanisms to improve them.
The EDs are modelled as two queueing systems each with a tandem buffer and a 
service centre.
The performance measures are then used as the utilities of the game.
The novelty of the queueing model here is a contribution not only the game 
theoretic literature but also to the queueing theoretic literature.
To the authors knowledge, no such model of a tandem queueing model with a pair 
of parameters for the buffer has been considered.
Although our research is motivated by the particular EMS-ED example, our 
developed modelling framework and behavioural insights has application to 
similar systems across a range of sectors and settings.

% Sign posting
This paper consists of two main sections.
Section \ref{sec:queueing_model} presents a novel queueing model for a hospital
with two types of patients and two waiting zones.
A detailed description of how to acquire the performance measure formulas of 
such queueing system is given.
Section \ref{sec:model_overview} gives an overview of the game theoretic model
and several
theoretic results pertaining to the performance measures of this model which 
are used to build the utilities of the game.
